Connecting R with D3 for dynamic graphics, to explore multivariate data with tours

### 2019-03-04 paper-tourrd3.Rmd
link to app code to Ursulas page

The code is available at [https://github.com/makipp/TourrGuiD3](https://github.com/makipp/TourrGuiD3), and the source material for this paper is available at [https://github.com/dicook/paper-tourrd3](https://github.com/dicook/paper-tourrd3).

>>>>

The code is available at [https://github.com/uschiLaa/tourrGUID3](https://github.com/uschiLaa/tourrGUID3), and the source material for this paper is available at [https://github.com/dicook/paper-tourrd3](https://github.com/dicook/paper-tourrd3).

### 2019-03-04 paper-tourrd3.tex
link to app code to Ursulas page

\begin{Schunk}
\begin{Sinput}
library(tourr)
# quartz() # to display on a Mac;
# X11() # For windows;
# The Rstudio graphics device is not advised
animate_dist(flea[, 1:6], center = TRUE)
\end{Sinput}
\end{Schunk}

@@

The code is available at \url{https://github.com/makipp/TourrGuiD3}, and
the source material for this paper is available at
\url{https://github.com/dicook/paper-tourrd3}.

>>>>

\begin{Schunk}
\begin{Sinput}
library(tourr)
# quartz() # to display on a Mac; X11() # For windows; The Rstudio graphics
# device is not advised
animate_dist(flea[, 1:6], center = TRUE)
\end{Sinput}
\end{Schunk}

@@

The code is available at \url{https://github.com/uschiLaa/tourrGUID3},
and the source material for this paper is available at
\url{https://github.com/dicook/paper-tourrd3}.
